%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Android Engineer} % Job title
    {Jobsity LLC} % Organization
    {Remote from Salvador, Brazil} % Location
    {Feb. 2022 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an Android application (Kotlin) in the field of cloud accounting..}
        \item {Performed at all mobile app lifecycle.}
        \item {Led features development.}
        \item {Designed to take the necessary actions to mitigate the security breach with CircleCI.}
        \item {Monitored application stability trendings.}
        \item {Created and documented internal processes to spread knowledge and standardize them across the team, such as the Release Process, the Feature Lead Tasks, and the Support Goalie Role.}
        \item {Mentored colleagues.}
        \item {Advised the team regarding the best practices on Android development.}
        \item {Worked with MVVM and MVP architecture pattern, Retrofit, Room, Dagger2, Material Components, Kotlin Coroutines, Firebase App, CircleCI, GitHub Enterprise.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Android Engineer} % Job title
    {BairesDev LLC} % Organization
    {Remote from Salvador, Brazil} % Location
    {Jun. 2021 - Feb. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Android SaMD (Software as a Medical Device) applications using Kotlin and Java side by side.}
        \item {Advised the team regarding the best practices on Android development.}
        \item {Integrated a Smart Insulin Pen with Android powered devices through Bluetooth.}
        \item {Guided the newcomer Android engineers over the project concepts.}
        \item {Worked with MVVM architecture pattern, Retrofit, Room, Dagger2, Material Components, Kotlin Coroutines, RxJava, Mockito, Roboeletric, BitBucket}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {CONDER} % Organization
    {Salvador, Brazil} % Location
    {Jul., 2014 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Planned and led the development of the applications and services hosted by the company.}
        \item {Developed and maintained Android applications and libraries built wither with Java or Kotlin.}
        \item {Developed and maintained a WPA Flutter application.}
        \item {Developed and maintained web map applications based on the ArcGIS platform.}
        \item {Developed web applications with .NET and ASP.NET.}
        \item {Main engineer in charge to automate geoprocessing task creating Python scripts}
        \item {Responsible to set up the company's first CI server (Jenkins CI), advocate for it, and spread the culture of continuous integration across the functional units.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Principal Software Engineer} % Job title
    {COMTECNO} % Organization
    {Salvador, Brazil} % Location
    {Dec. 2012 - Jul. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed, tested, and maintained the worldwide Motorola homescreen app, using Android with Java and Jenkins.}
        \item {Worked with Android platform customization, modifying the AOSP (Android Open Source Project) to compile the ROM and ship it to ARM devices.}
        \item {Customized CyanogenMOD and Odroid firmware, and made contributions to their community.}
        \item {Wrote low-level Dalvik bytecode.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Junior Software Engineer} % Job title
    {Motorola Mobility} % Organization
    {Jaguariuna, Brazil} % Location
    {Aug. 2010 - Aug. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed, tested, and maintained the worldwide Motorola homescreen app, using Android with Java and Jenkins.}
        \item {Worked with Android platform customization, modifying the AOSP (Android Open Source Project) to compile the ROM and ship it into ARM devices.}
        \item {Created an app to support Program Managers to set up the homescreen initial configuration for retail partners.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
